## Import packages
```{r}
library(dplyr)
library(RPostgreSQL)
library(tidyverse)
```
## Connect to database, please change the working directory below
```{r}
setwd("C:/Users/Huy/Desktop")
assertthat::assert_that(file.exists('dbconnect.txt'),
  msg = "Your connection file is missing.")
con_file <- readr::read_lines('dbconnect.txt')
con <- RPostgreSQL::dbConnect(
             PostgreSQL(),
             host = con_file[1],
             port = con_file[2],
             user = con_file[3],
         password = con_file[4],
           dbname = con_file[5])
```
## Census data 
### Import census data
```{r}
data <- readr::read_csv("C:\\Huy\\non-bike data\\CensusLocalAreaProfiles2016.csv")
```
### Remove empty columns
```{r}
data <- data[!apply(is.na(data) | data == "", 1, all),]
```
### Add Area ID, Area in Km, and Population density. Name the data frame "demographics"
```{r}
newdata <- subset(data, data$ID == 1 | data$ID == 95,
              select = c(ID, 3:24))
newdata <- t(newdata)
colnames(newdata) <- c("population", "median_age")
newdata <- newdata[-1,]
area_id  <-
  c("AR","CBD","DS","FAIR","GW","HS","KC","KERR","KIL","KITS","MARP","MP","OAK","RC","RP","SHAU","SC","STR","SUN",
    "VF","WE","WPG")
newdata <- cbind(area_id, newdata)
area_in_km <- c(3.7, 4.67, 9.08, 3.63, 4.75, 8.33, 7.25, 6.61, 6.93, 6.36, 6.57, 3.72, 4.02, 8.1, 4.93, 4.48, 2.18, 4.37, 6.57, 5.5, 2.26, 5.3)
newdata <- cbind(area_in_km, newdata)
newdata <- data.frame(newdata,stringsAsFactors = FALSE)
newdata <- type_convert(newdata)
newdata <-
  newdata %>%
  mutate(density = population / area_in_km)
demographics <- newdata
```
### Import Demographics to PostgreSQL
```{r}
dbWriteTable(con, "demographics", demographics, overwrite = TRUE)
```
## Bike Station Data
### Import bike station data
```{r}
data <- readr::read_csv("C:\\Huy\\bike\\stations.csv")
```
### Remove empty columns and NA values
```{r}
data <- data[!apply(is.na(data) | data == "", 1, all),]
```
### Remove:
    - station 33 (missing coordinates), station 1000 (temporary location, no coordinates),
    - column "style" (NA values), and column "operative" (only one value "True")
    - Cell[127,1] (special characters that cause an error in the importation to PostgreSQL)
```{r}
newdata <- subset(data,!data$`Station ID` == 1000)
newdata <- subset(newdata,!newdata$`Station ID` == 33)
newdata <- subset(newdata, select = -c(style, operative))
newdata[127,1] <- "0197 1st & Scotia"
```
### Rename column label to lower case letters. Name the data frame "stations"
```{r}
colnames(newdata) <- c("name","station_id","area_id","lat","lon","total_slots","free_slots","avl_bikes")

stations <- data.frame(newdata)
```
### Import "stations" to PostgreSQL
```{r}
dbWriteTable(con, "stations", stations, overwrite = TRUE)
```
## Trip history Data, January - July 2019
### Import Mobi Trip History Data to PostgreSQL
```{r}
data <- readr::read_csv("C:\\Huy\\bike\\Mobi_System_Data_2019.csv")
dbWriteTable(con,"trips",data,overwite = TRUE)
```
```{r}

```


